The Astropy Project

### 2017-11-20 main.tex
added section on support

@@

%\subsection{Support of Astropy}
% Removing unless this gets written about in
% a later version
% This section should be a straight forward/factual description of the current
% funding and support provided to astropy with the purpose of explaining the
% current structure to the community

>>>>

\section*{\textit{Notes and guidelines (to be removed)}}

\begin{itemize}
   \item The goal is to produce a brief and informative paper that covers major
        \astropy principles not mentioned in the first paper, the core v2.0
        package, and infrastructure in \astropy project to support development
        in \python.
    \item We don't plan on including code in this paper, but if you think you
        will need to include code in your section, please add it to a separate
        \python module (.py file) and include it in this repository.
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename}
        not ``Figure''
    \item Use \escapecmd{\astropypkg} for the astropy package,
        \escapecmd{\astropy} for the astropy project, \escapecmd{\python} not
        ``Python''
    \item If your subpackage was included in Paper I, then please just include a
        note on what the package does, a reference to paper I, and any new major
        updates to your package
    \item If your subpackage was not included, then please describe the
        subpackage on level with what was in the first paper, and highlight any
        major features in it. Typical length should be equivalent to one page
        (single-column).
    \item Please make sure you are logged into Overleaf or pushing a commit with
        your information to be able to track the contributors to the paper.

\end{itemize}

\section*{Global TODO items}
\begin{itemize}
    \item \sout{subpackage not sub-package!} BMS: checked as done 13/11
    \item spell check!
    \item check consistent astropy usage
\end{itemize}

@@

\subsection{Support of Astropy}

The \astropy project, as of the v2.0 release, does not receive any direct financial support for
the development of the \astropypkg.  Development of the \astropypkg is supported
through contributions by individuals to work on astropy in their own personal
time, contributions from individuals or groups to work on \astropy as 
part of a research project, or contributions from institutes that allocate 
people to work on \astropy. 
A list of organizations that have contributed to \astropy
are listed in the Acknowledgements.  
Different models have been proposed for the support of astropy 
(ie. \cite{2016arXiv161003159M}), 
but a sustainable, community-based model has not yet been established.
The astropy project has the ability to accept financial contributions 
(individual or institutes) through the NumFOCUS organization\footnote{NumFOCUS 
is a 501(c)(3) nonprofit that supports and promotes world-class, innovative, 
open source scientific computing.},  
which generally covers the direct costs incurred by the \astropy project
along with supporting

% Removing unless this gets written about in
% a later version
% This section should be a straight forward/factual description of the current
% funding and support provided to astropy with the purpose of explaining the
% current structure to the community
